### 2011-10-28 docs/src/manual.tex
markdown support added to CurryDoc

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.1}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of October 12, 2011\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

>>>>

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.1}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of October 28, 2011\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

The documentation comment for the module (i.e., the documentation
comment at the beginning of the module before the module header)
can be formatted with
\href{http://en.wikipedia.org/wiki/Markdown}{Markdown's syntax}\index{markdown}
provided that the
\href{http://johnmacfarlane.net/pandoc/}{pandoc}\index{pandoc}
 tool is installed.
If \code{pandoc} is not installed, one should run CurryDoc
with the parameter \ccode{--nopandoc}.
